HerMES: Spatially resolved ALMA Imaging of {\it Herschel}$^{\dagger}$-selected Dusty Star-forming Galaxies

### 2015-01-22 LaTeX/ms.tex
Sort model fits by RA
Edo Ibar comments
Very minor.

\begin{figure*}[!tbp] 
    \begin{centering}
%\epsscale{1.00} 
%\includegraphics[width=\textwidth]{cutouts_dec17.png}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS03_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS03_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS03_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS08_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS08_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS08_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS09_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS09_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS09_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS10_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS10_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS10_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS02_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS02_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS02_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS04_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS04_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS04_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS01_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS01_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS01_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS11_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS11_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS11_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS12_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS12_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS12_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS04_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS04_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS04_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS13_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS13_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS13_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HCOSMOS01_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HCOSMOS01_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HCOSMOS01_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HCOSMOS02_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HCOSMOS02_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HCOSMOS02_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HELAISS02_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HELAISS02_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HELAISS02_residual_bestfit.pdf}
\end{centering}

%\begin{figure*}[!tbp] 
%    \begin{centering}
%%\epsscale{1.00} 
%%\includegraphics[width=\textwidth]{cutouts_dec17.png}
%\end{centering}
%
%\caption{ Continued.}
%\addtocounter{figure}{-1}
%
%\end{figure*}
%
%\begin{figure*}[!tbp] 
%    \begin{centering}
%%\epsscale{1.00} 
%%\includegraphics[width=\textwidth]{cutouts_dec17.png}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS12_optical_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS12_model_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS12_residual_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS04_optical_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS04_model_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS04_residual_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS13_optical_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS13_model_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS13_residual_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HELAISS02_optical_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HELAISS02_model_bestfit.pdf}
%\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HELAISS02_residual_bestfit.pdf}
%\end{centering}
%
%\caption{ Continued.}
%\addtocounter{figure}{-1}
%
%\end{figure*}

@@

@@

@@

The key components of the model are the mass density profile of the lenses,
$\rho_{\rm lens}\,(r)$, the number density of lenses as a function of mass and
redshift, $n_{\rm lens}\,(M, \, z)$), the redshift distribution of the sources,
$dN_{\rm source}/dz$, and the intrinsic luminosity function of the sources,
$dn_{\rm source}/dS_{870}^\prime)$.  The latter component is the least certain
component and also has the strongest impact on the predicted apparent
luminosity function.  For these reasons, we fix all components of the model
except the shape of the intrinsic luminosity function.  Our goal is to take
luminosity functions that can successfully fit observed faint DSFG number
counts \citep{Karim:2013lr} and test whether they lead to predicted
magnification factors consistent with our ALMA and SMA observations.

@@

    \item 20/29 {\it Herschel} DSFGs break down into multiple ALMA
        counterparts.  Of the 9 isolated systems, 5 are strongly lensed by
        factors of 5-10.  After correcting for amplification, the brightest
        source in the sample has $S_{870}^\prime = 15.42 \pm 0.43\,$mJy.  There
        is a weak trend towards even higher multiplicity at the highest total
        $S_{870}$ flux densities.

>>>>

@@

\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HELAISS02_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HELAISS02_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HELAISS02_residual_bestfit.pdf}

@@

\begin{figure*}[!tbp] 
    \begin{centering}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS12_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS12_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS12_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS04_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS04_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS04_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS13_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS13_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HECDFS13_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS04_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS04_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS04_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS02_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS02_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS02_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS11_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS11_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS11_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS10_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS10_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS10_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS01_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS01_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS01_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS09_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS09_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS09_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS08_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS08_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS08_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS03_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS03_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HADFS03_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HCOSMOS02_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HCOSMOS02_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HCOSMOS02_residual_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HCOSMOS01_optical_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HCOSMOS01_model_bestfit.pdf}
\includegraphics[width=0.162\textwidth]{../Figures/modelfit/HCOSMOS01_residual_bestfit.pdf}
\end{centering}

@@

The key components of the model are the mass density profile of the lenses,
$\rho_{\rm lens}\,(r)$, the number density of lenses as a function of mass and
redshift, $n_{\rm lens}\,(M, \, z)$, the redshift distribution of the sources,
$dN_{\rm source}/dz$, and the intrinsic luminosity function of the sources,
$dn_{\rm source}/dS_{870}^\prime$.  The latter component is the least certain
component and also has the strongest impact on the predicted apparent
luminosity function.  For these reasons, we fix all components of the model
except the shape of the intrinsic luminosity function.  Our goal is to take
luminosity functions that can successfully fit observed faint DSFG number
counts \citep{Karim:2013lr} and test whether they lead to predicted
magnification factors consistent with our ALMA and SMA observations.

@@

    \item 20/29 {\it Herschel} DSFGs break down into multiple ALMA
        counterparts.  Of the 9 isolated systems, 5 are strongly lensed by
        factors of 5-10.  After correcting for amplification, the brightest
        source in the sample has $S_{870} = 15.42 \pm 0.43\,$mJy.  There
        is a weak trend towards even higher multiplicity at the highest total
        $S_{870}$ flux densities.
